---
title: 'Quiz: Exploring the Data'
author: "Eddo W. Hintoso"
date: "October 21, 2015"
output:
  pdf_document: default
  html_document:
    highlight: zenburn
    theme: readable
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# library(knitr)
# opts_chunk$set(cache = TRUE)
library(dplyr)
```

**1. After untaring the the dataset, how many files are there (including the documentation pdfs)?**

7

---

**2. The data files are in what format?**

`.json`

---

**3. How many lines of text are there in the reviews file (in orders of magnitude)?**

```{r}
yelpReviewRDS <- readRDS('../yelp_dataset_challenge_academic_dataset/yelp_academic_dataset_review.rds')
dim(yelpReviewRDS)
```

One million

---

**4. Consider line 100 of the reviews file. “I’ve been going to the Grab n Eat for almost XXX years”**

```{r}
yelpReviewRDS$text[100]
```

20

---

**5. What percentage of the reviews are five star reviews (rounded to the nearest percentage point)?**

```{r}
100 * length(yelpReviewRDS$stars[yelpReviewRDS$stars == 5]) / length(yelpReviewRDS$stars)
```

37%

---

**6. How many lines are there in the businesses file?**

```{r}
yelpBusinessRDS <- readRDS('../yelp_dataset_challenge_academic_dataset/yelp_academic_dataset_business.rds')
dim(yelpBusinessRDS)
```

About 60 thousand

---

**7. Conditional on having an response for the attribute "Wi-Fi", how many businesses are reported for having free wi-fi (rounded to the nearest percentage point)?**

```{r}
100 * length(na.omit(yelpBusinessRDS$`attributes.Wi-Fi`[yelpBusinessRDS$`attributes.Wi-Fi` == "free"])) / length(na.omit(yelpBusinessRDS$`attributes.Wi-Fi`))
```

40%

---

**8. How many lines are in the tip file?**

```{r}
yelpTipRDS <- readRDS('../yelp_dataset_challenge_academic_dataset/yelp_academic_dataset_tip.rds')
dim(yelpTipRDS)
```

About 500 thousand

---

**9. In the tips file on the 1,000th line, fill in the blank: "Consistently terrible ______"**

```{r}
yelpTipRDS$text[1000]
```

service

---

**10. What is the name of the user with over 10,000 compliment votes of type "funny"?**

```{r}
yelpUserRDS <- readRDS('../yelp_dataset_challenge_academic_dataset/yelp_academic_dataset_user.rds')
subset(yelpUserRDS, compliments.funny > 10000)$name
```

Brian

---

**11. Create a 2 by 2 cross tabulation table of when a user has more than 1 fans to if the user has more than 1 compliment of type "funny". Treat missing values as 0 (fans or votes of that type). Pass the 2 by 2 table to fisher.test in R. What is the P-value for the test of independence?**

```{r}
yelpUserRDS$compliments.funny[is.na(yelpUserRDS$compliments.funny)] <- 0
yelpUserRDS$fans[is.na(yelpUserRDS$fans)] <- 0
cross.table <- matrix(c(sum(yelpUserRDS$compliments.funny > 1),
                        sum(yelpUserRDS$compliments.funny <= 1),
                        sum(yelpUserRDS$fans > 1),
                        sum(yelpUserRDS$fans <= 1)),
                      nrow = 2)
fisher.test(cross.table)
```

less than .001